Highly Available Transactions: Virtues and Limitations

### 2013-03-30 writeup/hat-analysis.tex
Couple very minor fixes

To begin, we present achievable semantics, offering proof-of-concept
algorithms to demonstrate feasibility. These guarantees are fairly
straightforward and have been introduced---albeit with greater brevity
and discussion elided---in a preliminary workshop
paper~\cite{hat-hotos}. In our examples, we exclusively consider read
and write operations. We denote a write of value $v$ to data item $d$
as $w_d(v)$ and a read from data item $d$ returning $v$ as $r_d(v)$
and assume that all data items have the null value, $\bot$, at
database initialization. Unless otherwise specified, all example
transactions commit.

>>>>

To begin, we present achievable semantics, offering proof-of-concept
algorithms to demonstrate feasibility. These guarantees are fairly
straightforward and have been introduced---albeit with greater brevity
and discussion omitted---in a preliminary workshop
paper~\cite{hat-hotos}. In our examples, we exclusively consider read
and write operations. We denote a write of value $v$ to data item $d$
as $w_d(v)$ and a read from data item $d$ returning $v$ as $r_d(v)$
and assume that all data items have the null value, $\bot$, at
database initialization. Unless otherwise specified, all example
transactions commit.
